Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-06-09 paper/referee_reply1.txt

Reply) The implementation of the stellar mass stripping model is indeed crude and to some extent the self-inconsistency pointed out by the referee is inescapable: we are after all not providing a model for the true evolution of post-infall stellar mass, but instead we are grafting an approximate treatment that is intended to approximate the impact of tidal stripping in a statistical sense. The modification to the SMF is rather small; we have added a comment to that effect in the text.

6) A complementary method for studying the size-halo connection is to constrain correlations of galaxy size with halo properties *at fixed stellar mass*, which has been done using both weak lensing (e.g. Sonnenfeld et al 2015, Sonnenfeld & Leauthaud 2017) and galaxy dynamics (e.g. Desmond 2016, 2017). These are means of testing disk models such as Dutton et al 2007 & 2011 which the authors mention. It would be helpful to provide more information on how the Rvir-based model presented here relates to this alternative method. For example, since on average M* is positively correlated with Rpeak by AM, and empirically Reff is positively correlated with M*, then the model in which Reff depends only on M* (Sec 3.2.1) will also positively correlate Reff with Rpeak. It is not clear how this correlation differs from Reff=0.01*Rpeak, or in other words how the latter assumption correlates Reff with halo properties at fixed M*. It would be interesting to see 1) The Reff-Rpeak relation implied by the model in Sec 3.2.1, and/or 2) The correlation of Reff with halo mass or concentration at fixed M* implied by Reff=0.01*Rpeak. Understanding these different approaches will be of great help in devising a unified model for the size-halo connection.

Reply)  We have verified the correlation between R_1/2 and Mvir at fixed M* in present day centrals, and added a paragraph to Section 6 with the suggested references. The new text is repeated below for convenience.

---
In closely related work, efforts to constrain correlations of galaxy size with halo properties at fixed stellar mass have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}. Our results complement these previous studies in that forward-modeling galaxy observables directly into simulations provides a rigorous means by which one can test hypotheses of correlations implemented at fixed halo properties. In our fiducial model with $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals there exists a significant positive correlation between present day mass and galaxy size at fixed stellar mass; these alternative methods are a natural testbed for future tests of the basic conclusions drawn here based on two-point clustering.
---

### 2018-06-09 paper/galsize_paper.tex
Added reply and revisions for major comment 6

>>>>

In closely related work, efforts to constrain correlations of galaxy size with halo properties at fixed stellar mass have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}. Our results complement these previous studies in that forward-modeling galaxy observables directly into simulations provides a rigorous means by which one can test hypotheses of correlations implemented at fixed halo properties. In our fiducial model with $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals there exists a significant positive correlation between present day mass and galaxy size at fixed stellar mass; these alternative methods are a natural testbed for future tests of the basic conclusions drawn here based on two-point clustering.
